NOSQL\\ BEST PRACTICES

### 2018-03-28 pgconfus2018/presentation.tex
Fix typo and date
Add insert benchmarks and cat

    \vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\color{black} 12-05-2017}%

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Document slide: in the DB or on the app?}

@@

@@

        \includegraphics[width=0.75\textwidth,center]{json_vs_jsonb.png}

@@

        \includegraphics[width=0.75\textwidth,center]{jsonb_vs_relation.png}

@@

>>>>

    \vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\color{black} 29-03-2018}%

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Document slice: in the DB or on the app?}

@@

\fontsize{13pt}{14}\selectfont
\section{Insert workload}
\fontsize{17pt}{18}\selectfont

@@

        \includegraphics[width=0.75\textwidth,center]{json_vs_jsonb_insert.png}

@@

        \includegraphics[width=0.75\textwidth,center]{jsonb_vs_relation_insert.png}

\fontsize{13pt}{14}\selectfont
\section{Read workload}
\fontsize{17pt}{18}\selectfont

        \includegraphics[width=0.75\textwidth,center]{json_vs_jsonb_read.png}

        \includegraphics[width=0.75\textwidth,center]{jsonb_vs_relation_read.png}

@@

        \includegraphics[width=0.75\textwidth,center]{cat.png}
